### 2016-08-26 reviewer_reply.txt

- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - 
Reviewer 1:
- - - - - - - - - - - - - - - - - - - - - - - - - - - - - -

Dear reviewer,

Thank you very much for you valuable feedback and detailed comments.
They have been very useful. To address your comments, we list
the ones that require our modification below and provide our answer.

- "To improve the article and considering that already others authors have faced problems similar even if different, the reviewer suggests to enrich the bibliography with others articles. For instance, in the introduction could be possible to cite these:

1) ...'An Intelligent and High Efficiency Street Lighting System Isle Based on...' ...
2) ...'A Fully Controlled Street Lighting System Isle Based on...' ...
3)  ...'A New Acquisition and Imaging System for Environmental...' ...
4) ...'A New Remote and Automated Control System for the Vineyard...'
5) ...'FingerScanner: Embedding a Fingerprint Scanner in a Raspberry Pi' "

We consider relevant the suggested references. Still, we include different use
cases and journal versions of articles with similar core ideas behind. Thus, after
reading them, references 2-3) and 5) are now used as references 11-13)
in the new revised manuscript to improve our introduction. Besides these, in the
revised manuscript, references 9-10) have been included to enhance
the quality of it.

- "As minor revision please check and correct the following rows: 62, 171, 546, 705."

We have corrected all the typos by proof-reading the manuscript.
Also, we have entirely rewritten a few of the sentences
indicated as misunderstanding, but in most cases made the corrections as suggested.

@@

Dear reviewer,

Thank you for your time with the revision.

- - - - - - - - - - - - - - - - - - - - - - - - - - - - - - 
Reviewer 3:
- - - - - - - - - - - - - - - - - - - - - - - - - - - - - -

Dear reviewer,

Thank you very much for your valuable feedback and suggested citations.
To address your comments, we list the ones that require our modification
below and provide our answer. For simplicity, we list them by type
of comment

- Comments of the form: "The suggestions by :

...
Page XX,
Line YY
Line ZZ
...
"

We have corrected all the typos by proof-reading the manuscript.
Also, we have entirely rewritten a few of the sentences
indicated as misunderstanding, but in most cases made the corrections as suggested.

- Comment of the form: "Suggest to add:

1) Cox, S. ...'Iridis-pi: a low-cost, compact demonstration cluster'...
2) Raspberry Pi Foundation ...'The Making of Pi,'...
3) D'Orazio C ...'Data Exfiltration from Internet of Things Devices: iOS Devices as Case Studies'...

"

These citations have helped to better address the
prior work for a Raspberry Pi testbed. We think 1) and 2) are relevant
references and are used in the new revised manuscript as references 9-10).
Nevertheless, but we do not see how to fit the reference
"Data Exfiltration from Internet of Things Devices: iOS
Devices as Case Studies" which we think is related to IoT, but not very much
to Raspberry Pi, testbeds or network coding. Besides these, references 11-13)
in the new revised manuscript, have been included to enhance the quality of it.

### 2016-08-26 appendix.tex
Final revised version. Few corrections, typos and removing an extrablank page

In case the \texttt{umount ----recursive} command shows the \texttt{invalid option}
message, an alternative is to manually unmount all the partitions used
during the \texttt{chroot} environment. The directories must be unmounted in
the reverse order as when they were mounter. These commands are:
%In case the \texttt{umount ----recursive} command fails given that a version
%higher than 2.22 for \texttt{util-linux} is not available,
%a possible option is to manually umount all the partitions used during the
%\texttt{chroot} environment. The directories must be unmounted in the reverse
%order as when they were mounted. These commands are:

@@

\subsection{Paramiko Package Update}
\label{sec:paramiko}
In case Paramiko version 1.15.1 or higher is not installed, we may observe
a key exchange algorithm error when trying to log in through \ac{SSH} to a
Raspi. In this case, it might be necessary to update the Paramiko package
that Fabric uses for this purpose and verify this by running:

@@

This should allow to make \ac{SSH} connections with Fabric by using the proper
key exchange algorithms through Open SSH.

>>>>

In case the \texttt{umount ----recursive} command shows the \texttt{invalid option}
message, an alternative is to manually unmount all the partitions used
during the \texttt{chroot} environment in the reverse order which they were mounted.
These commands are:
%In case the \texttt{umount ----recursive} command fails given that a version
%higher than 2.22 for \texttt{util-linux} is not available,
%a possible option is to manually umount all the partitions used during the
%\texttt{chroot} environment. The directories must be unmounted in the reverse
%order as when they were mounted. These commands are:

@@

\subsection{Paramiko Package Update}
\label{sec:paramiko}
In case Paramiko version 1.15.1 or higher is not installed, we may observe
a key exchange algorithm error when trying to log in through \ac{SSH} to a
Raspi with Open SSH. In this case, it might be necessary to update the Paramiko
package that Fabric uses to remove this error by running:

@@

### 2016-08-26 introduction.tex
Final revised version. Few corrections, typos and removing an extrablank page

Introduced by Ahlswede et al. \cite{ahlswede2000network}, network coding constitutes a paradigm shift in the way how researchers and industry understand and operate networks, by changing the role of intermediate relays in the process of transmission of information. Relays are no longer limited to storing and forwarding data, but also take part in the coding process, through a process called recoding, where the relay generates new linear combinations of incoming coded packets without previously decoding the data. Network coding allows the increase of throughput, reliability, security and delay performance of the networks. In our previous works, we have shown that \ac{RLNC} \cite{koetter2003algebraic,ho2006random} is able to satisfy the aforementioned technical requirements. We have actually shown how to increase the throughput \cite{pahlevani2013playncool}, reduce the delay \cite{szabo2015towards} or support heterogeneity for coding enabled communication nodes \cite{lucani2014fulcrum}.

In all these prior works, the C++11 Kodo library \cite{kodo2011pedersen} was used as the common building block containing the basic \ac{RLNC} functionalities. However, most of the work was focusing on small mesh networks with a handful of communication nodes, though the expected scenarios are fairly beyond this order of magnitude. Moreover, despite this successful deployment in real systems, many of these protocols and contributions have been implemented in separate testbeds and the experiences are hard to reproduce. Furthermore, deploying a large-scale and configurable testbed for networking and storage can be challenging, not only due to the inherent costs of the hardware, but due to maintenance challenges and ability to replicate results consistently. The latter requires not only the devices to run the same \ac{OS}, but also have exactly the same configurations and software packages. Hence, there is a need in evaluating large scale network deployments of low cost devices in a quick, easy-to-deploy, reproducible and maintainable fashion.

The emergence of powerful and inexpensive single-board computers running full versions of a standard \ac{OS} from many possible opens new possibilities in this area. This not only allows to seamlessly develop implementations that are compatible with higher end devices but also allows the reuse stable software from widely-used \ac{OS}. For example, the work in \cite{cox2014iridis} provides a detailed description of a \ac{Raspi}~\cite{making_of_pi} testbed ideal for educational applications. Here the authors also include computational, throughput and storage benchmarks to assess its performance. However, this work indicates only a basic description of how to set up the required software and also mentions that its maintenance could be time-demading. Moreover, this work does not consider possible network coding applications. Different studies of \ac{IoT} applications consider using the \ac{Raspi} for data processing: In \cite{leccese2014smartcity}, the \ac{Raspi} is the processing unit that coordinates and controls the activity of a public road isle of lamps and reports it to a monitoring center. A use case regarding remote environment surveillance is presented in \cite{leccese2014newimaging}, where the \ac{Raspi} reports air pressure, humidity and temperature of the locations of cultural paintings plus high-resolution images of the paintings themselves. This data is sent to a monitoring center to ensure the preservation of the paintings. Further, authors in \cite{sapes2016finger} utilize the \ac{Raspi} to act as the data server in a finger scanning application that collects the fingerprints. Even though all these applications consider the use of the \ac{Raspi} as a core block, they provide few to no description of their procedures to configure the \ac{Raspi} making their discussed results difficult to reproduce. Moreover, these applications become cumbersome to maintain as their considered systems could potentially scale when aiming to serve more users. Furthermore, the current way that the data is sent in the considered networks for these \ac{IoT} applications will not be feasible in future 5G systems as mentioned previously.

>>>>

Introduced by Ahlswede et al. \cite{ahlswede2000network}, network coding constitutes a paradigm shift in the way how researchers and industry understand and operate networks, by changing the role of intermediate relays in the process of transmission of information. Relays are no longer limited to storing and forwarding data, but also take part in the coding process, through a process called recoding, where the relay generates new linear combinations of incoming coded packets without previously decoding the data. Network coding allows the increase of throughput, reliability, security and delay performance of the networks. In previous works, we have shown that \ac{RLNC} \cite{koetter2003algebraic,ho2006random} is able to satisfy the aforementioned technical requirements. We have actually shown how to increase the throughput \cite{pahlevani2013playncool}, reduce the delay \cite{szabo2015towards} or support heterogeneity for coding enabled communication nodes \cite{lucani2014fulcrum}.

In our prior works, the C++11 Kodo library \cite{kodo2011pedersen} was used as the common building block containing the basic \ac{RLNC} functionalities. However, most of the work was focusing on small mesh networks with a handful of communication nodes, though the expected scenarios are fairly beyond this order of magnitude. Moreover, despite this successful deployment in real systems, many of these protocols and contributions have been implemented in separate testbeds and the experiences are hard to reproduce. Furthermore, deploying a large-scale and configurable testbed for networking and storage can be challenging, not only due to the inherent costs of the hardware, but due to maintenance challenges and ability to replicate results consistently. The latter requires not only the devices to run the same \ac{OS}, but also have exactly the same configurations and software packages. Hence, there is a need in evaluating large scale network deployments of low cost devices in a quick, easy-to-deploy, reproducible and maintainable fashion.

The emergence of powerful and inexpensive single-board computers running full versions of a standard \ac{OS} from many possible opens new possibilities in this area. This not only allows to seamlessly develop implementations that are compatible with higher end devices, but also permits the reuse of stable software from widely-used \ac{OS}. For example, the work in \cite{cox2014iridis} provides a detailed description of a \ac{Raspi}~\cite{making_of_pi} testbed ideal for educational applications. Here the authors present computational speed benchmarks, inter-node communication throughput and memory card writing speeds for data storage to assess the testbed performance. However, this work indicates only a basic description of how to set up the required software and also mentions that its maintenance could be time-demading. Moreover, this work does not consider possible network coding applications. Different studies of \ac{IoT} applications consider using the \ac{Raspi} for data processing: In \cite{leccese2014smartcity}, the \ac{Raspi} is the processing unit that coordinates and controls the activity of a public road isle of lamps and reports it to a monitoring center. A use case regarding remote environment surveillance is presented in \cite{leccese2014newimaging}, where the \ac{Raspi} reports air pressure, humidity and temperature of the locations of cultural paintings plus high-resolution images of the paintings themselves. This data is sent to a monitoring center to ensure the preservation of the paintings. Further, authors in \cite{sapes2016finger} utilize the \ac{Raspi} to act as the data server in a finger scanning application that collects the fingerprints. Even though all these applications consider the use of the \ac{Raspi} as a core block, they provide few to no description of their procedures to configure the \ac{Raspi}. Moreover, these applications become cumbersome to maintain as their considered systems could potentially scale when aiming to serve more users. Furthermore, the current way that the data is sent in the considered networks for these \ac{IoT} applications will not be feasible in future 5G systems as mentioned previously.
